\huge Tor's Usability for Censorship Circumvention

### 2016-06-01 pets2017-paper/pets2017-paper.tex
dave's comments: minor typo changes

\subsubsection{Time to Success} 
Time to success is defined as the time until the first successful connection to Tor. Non-finishing participants are assigned the maximum experiment time of 40:08.  Our changes to the interface had a significant impact in reducing the time participants took to successfully connect to Tor (Mann--Whitney $Z = -1.84$, $p = 0.0328$, $r= 0.172$). The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$). 
Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_clamped} shows their distribution.

@@

\subsubsection{Active Time} 
We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges} and summarize where they spent their time in Appendix~\ref{all-participant-times}. Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant. The bar represents a path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.

@@

We performed a one-tailed Mann--Whitney test to compare the amount of active configuration time between participants who used the new interface and the participants who used the old interface. Our changes to the interface reduced the time participants spent configuring the interface (Mann--Whitney $Z = -3.28$, $p = 0.000516$, $r = 0.307$). Table Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.

@@

5 Participants downloaded Tor Browser:  P115 (Fig.~\ref{softsonic}), P116 (Fig.~\ref{techspot}), P117, data not used (Fig.~\ref{mirror}), P118, data not used (Fig.~\ref{downloadio}), and P119, data not used (Fig.~\ref{driverupdate}).

@@

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}
\caption{P115 downloaded Tor Browser from Softsonic, a reputable-looking but
unconfirmed site.}
\label{softsonic}
\end{figure}

>>>>

\subsubsection{Time to Success} 
Time to success is defined as the time until the first successful connection to Tor. Non-finishing participants are assigned the maximum experiment time of 40:08.  Our changes to the interface had a significant impact in reducing the time participants took to successfully connect to Tor (Mann--Whitney $Z = -1.84$, $p = 0.0328$, $r= 0.172$; see Appendix~\ref{stat-tests}). The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$). 
Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_clamped} shows their distribution.

@@

\subsubsection{Active Time} 
We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
%and summarize where they spent their time in Appendix~\ref{all-participant-times}. 
Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant. The bar represents a path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.

@@

We performed a one-tailed Mann--Whitney test to compare the amount of active configuration time between participants who used the new interface and the participants who used the old interface. Our changes to the interface reduced the time participants spent configuring the interface (Mann--Whitney $Z = -3.28$, $p = 0.000516$, $r = 0.307$).  Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.

@@

5 Participants downloaded Tor Browser:  P115 (Fig.~\ref{softonic}), P116 (Fig.~\ref{techspot}), P117, data not used (Fig.~\ref{mirror}), P118, data not used (Fig.~\ref{downloadio}), and P119, data not used (Fig.~\ref{driverupdate}).

@@

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}
\caption{P115 downloaded Tor Browser from Softonic, a reputable-looking but
unconfirmed site.}
\label{softonic}
\end{figure}
